\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-08 doc/paper.tex
Fixes 146 but bears revision.

	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
	chose the tree form for its inherent ability to represent the parent-children
	relationship of formulae as functions and their arguments, which could be yet
	more functions. By adapting this structure to accommodate a broad range of
	possibilities for nested functions, the branching factor depends alternatively
	on the number of arguments in a function and the number of possible functions
	observed as an argument in a function. \par

>>>>

	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
	chose the tree form for its inherent ability to represent the parent-children
	relationship of formulae as functions and their arguments, which could be yet
	more functions. By adapting this structure for a broad range of
	possibilities for nested functions, the branching factor depends alternatively
	on the number of arguments in a function and the number of possible functions
	observed as an argument in a function. \par

	Another of our options was to represent the call trees as simple text hierarchies. 
	Though this might work well for a single, uncomplicated call structure, we did not
	do this because our tool combined many of these call trees into a more complicated 
	structure. To capture the different relationships in the tree and to quantify the
	frequency of arguments, we would need to be more verbose in our description. As such, we
	decided that visualizing some dimensions was quicker than writing them out. 
	\par
